---
title: "Creating, updating & maintaining the statquotes data base"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating, updating & maintaining the statquotes data base}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(statquotes)
```

## Primary format for quotes file

The quotes are stored in the `data-raw/quotes_raw.txt` file. The script `data-raw/convert_quotes_to_rda.R` can be used to read these quotes and save them to `data/quotes.rda`, which is the main data file used in the package.

The `quotes_raw.txt` file uses the following format for each quotation.  Lines beginning with "%" are comments and ignored.  Other lines contain a "key:value" pair. The key is used to identify the right column when building the `quotes` dataframe:

```
% Comment
quo:This is a quotation.
src:Person or persons who said or wrote the quote.
cit:Citation for the original quote.
url:URL where the quote can be found (such as journal articles).
tag:Comma-separated tags to categorize the quote.
tex:TeX-formatted citation
```

Here is an example:

```
quo:A judicious man looks at Statistics, not to get knowledge, but to save himself from having ignorance foisted on him.
src:Thomas Carlyle
cit:Chartism, 1840, Chapter II, Statistics
url:https://en.wikisource.org/wiki/Chartism/Chapter_2
tag:data visualization
```

## LaTeX format for quotes file

The `statquotes` package originally arose from a LaTeX file, that Michael Friendly used to collect interesting quotations related to statistics, data visualization, history, software and other topics. This was designed to be a collection that a person could search, then copy/paste an appropriate one into a working LaTeX document.  The format of quotes was designed to use the LaTeX `epigraph` package:

```
\epigraph{You can see a lot, just by looking.}{Yogi Berra}
\epigraph{Every picture tells a story.}{Rod Stewart, 1971}
\epigraph{A picture is worth a thousand words.}{F. Barnard, 1927}
```

Each quote has some `text` and a `source` attribution, and so could be displayed in a document something like

> *You can see a lot, just by looking.* 
> --- Yogi Berra

Some of the quotes have manually-added `tags` to classify the quotes into groups. As many tags as desired can be added to a quote.

