---
title: "Creating, updating & maintaining the statquotes data base"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating, updating & maintaining the statquotes data base}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(statquotes)
```

`statquotes` items can be read and parsed by the `inst/readQuotes()` function in either text (`.txt`) or LaTeX (`.tex`) format. These are saved in the `inst/quotes.csv` file, which is then also saved in `data/quotes.RData`, the main data file used in the package. The function `readQuotes()` is not yet
exported.

## LaTeX format

`statquotes` originally arose from a LaTeX file, `quotes.tex`  that I used to collect interesting quotations
related to statistics, data visualization, history, software and other topics. This was designed to be a collection I could search, then copy/paste an appropriate one into a working LaTeX document.  The format
of quotes was designed to use the LaTeX `epigraph` package:

```
\epigraph{You can see a lot, just by looking.}{Yogi Berra}
\epigraph{Every picture tells a story.}{Rod Stewart, 1971}
\epigraph{A picture is worth a thousand words.}{F. Barnard, 1927}
```
Each quote has some `text` and a `source` attribution, and so could be displayed in a document something like

> *You can see a lot, just by looking.* 
> --- Yogi Berra

Overtime, I wanted to categorize these by `topic` and `subtopic`, so `\section{}` and `\subsection{}` were introduced into the `quotes.tex` file.

This results in what is the canonical form for a quotations file in LaTeX format.

```
\section{Data visualization}
\epigraph{You can see a lot, just by looking.}{Yogi Berra}

\subsection{Pictures}
\epigraph{Every picture tells a story.}{Rod Stewart, 1971}
\epigraph{A picture is worth a thousand words.}{F. Barnard, 1927}
...
```

## Text format

The following lines illustrate the text format, similar in most respects to the output of the `fortunes` package

```
%% Some sample quotes
%  ... to illustrate the format

## Data visualization
You can see a lot, just by looking.
--- Yogi Berra

### Pictures
Every picture tells a story.
--- Rod Stewart, 1971

A picture is worth a thousand words.
--- F. Barnard, 1927
```

In this format:

* Lines starting with `%` are treated as comments and ignored.
* Separate quotes are separated by one or more blank lines.
* Lines beginning with `##` are treated as defining a new section (`topic` in the database), which persists until the next section is started.
* Similarly, lines beginning with `###` define a new subsection (`suptopic`).
* Lines beginning with a word character give the text of a quotation. In this version of `readQuotes()`, the entire quote **must appear on one line** in the text file.
* Lines beginning with `--- ` give the source of the quotation, typically just a name, publication, year.





